Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-01-28 manuscripts/manuscript.Rmd
tweaking figure 4

```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4, cache=fig.cache, dev=c("pdf", "svg", "png")}

@@

legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box") 
grid.arrange(do.call(arrangeGrob, 
            lapply(list(p4a, p4b),
                   function(x) x + theme_bw() + theme(legend.position="none"))),
    legend,
    ncol = 2,
    widths = c(5,1))

>>>>

```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4.5, cache=fig.cache, dev=c("pdf", "svg", "png")}

@@

legend <- gtable_filter(ggplot_gtable(ggplot_build(p4a)), "guide-box") 
grid.arrange(do.call(arrangeGrob, 
            lapply(list(p4a, p4b),
                   function(x) x + theme_bw() + theme(legend.position="none"))),
    legend,
    ncol = 2,
    widths = c(5,1.5))
